Mariage Liciences Pre and Post Pandemic

### 2024-09-19 paper/paper.qmd
llm usage update

---
title: "My title"
subtitle: ""
author: 
  - Fatimah Yunusa
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)

data <- read_csv(here::here("data/analysis_data/analysis_data"))
```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @opendata.

The remainder of this paper is structured as follows. @sec-data....

@@

@@

Talk way more about it.

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

@@

# Appendix {-}

>>>>

---
title: "Mariage Liciences Pre and Post Pandemic"
subtitle: "Was there a difference? "
author: 
  - Fatimah Yunusa
thanks: "Code and data are available at: https://github.com/fatimahsy/Pandemic-Marriages-.git."
date: today
date-format: long
abstract: "This paper examines trends in marriage licenses in Toronto, focusing on the effects of the COVID-19 pandemic on marital patterns. Using a dataset of marriage license registrations from 2015-2023, we apply time series analysis and statistical comparisons to investigate shifts in marriage rates before, during, and after the pandemic. Our findings show a significant decline in licenses issued during the pandemic, followed by a sharp increase in the post-pandemic period. These results suggest that social disruptions caused by the pandemic have had lasting effects on marriage trends, potentially influencing future policy and service planning ."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data"))

We use @citeR and @opendata.

@@

Some of our data is of Marriage licences (@fig-marriage) from @opendatatoronto. The scatter plot (@fig-marriage) displays the number of marriage licenses issued in Toronto over time, spanning from before 2015 to approximately 2025. The graph shows relatively stable issuance of licenses between 2015 and 2019, with a noticeable drop around 2020, coinciding with the onset of the COVID-19 pandemic. Following this decline, there is a sharp increase in licenses after 2021, suggesting a recovery and potential backlog of marriages post-pandemic. The pronounced spike in recent years indicates a significant shift in marriage behavior, likely influenced by the social and economic impacts of the pandemic.

```{r}
#| label: fig-marriage
#| fig-cap: Marriage Licinces By Date
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

@@

\`\`\`

@@

# Appendix {.unnumbered}
